Verifying Demonstrations

### 2018-10-31 paper/DB-anon-cred.tex
added a comment command for simon (\simon) in orange, tested it in verification subsection.

Tamarin auto-prover validated the soundness and correctness properties (in negligible computation time) but does not terminate when trying to prove the security properties, that is to say, no trace violating the security properties is found, but the prover cannot conclusively validate that the properties are true. We are currently investigating with Tamarin interactive mode to hopefully validate the security properties as well.

\sonja{\subsection{Formal Verification} 
 verification with tamarin: there is no BC Schnorr in Tamarin,  [10]
assumed equivalence with Fiat-Shamir model. Not straightforward to
implement Schnorr in Tamarin due to a lack of expressiveness for
arithmetic needed to complement Diffie-Hellman. If not done now, left
for future work. }

>>>>

Tamarin auto-prover validated the soundness and correctness properties (in negligible computation time) but does not terminate when trying to prove the security properties, that is to say, no trace violating the security properties is found, but the prover cannot conclusively validate that the properties are true. We are currently investigating with Tamarin interactive mode to hopefully validate the security properties as well.
\simon{test by sonja}
%\sonja{\subsection{Formal Verification} 
%  verification with tamarin: there is no BC Schnorr in Tamarin,  [10]
% assumed equivalence with Fiat-Shamir model. Not straightforward to
% implement Schnorr in Tamarin due to a lack of expressiveness for
% arithmetic needed to complement Diffie-Hellman. If not done now, left
% for future work. }
